Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-25 draft.tex
not sure what i did

\begin{thm}
\label{T:compcentralizer}
Let $f: \fg \rightsquigarrow \fh$ and $g: \fh \rightsquigarrow \fl$ be maps of  $L_\infty$ algebras,
and let $\bold{f}: \bU_n \fg \to \bU_n \fh$ and $\bold{g}: \bU_n \fh \to \bU_n \fl$ denote the induced maps of factorization algebras.
\begin{enumerate} 
\item There is a natural map of factorization algebras
\[
(-\star-) : \bZ_n(g) \otimes \bZ_n(f) \to \bZ_n(g \circ f),
\]
given by definition~\ref{def:comp}, 
that models the canonical map 
\[
{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f).
\] 
\item If $f= \fg \stackrel{\id}\to \fg$, 
then the composition $(-\star-)$ makes $\bZ_n(\fg)$ into an 
augmented associative algebra {\em on the nose} in the 1-category of factorization algebras on~$\RR^n$,
and it models the center ${\frak Z}_n(\fg)$ as an $E_1$ algebra in $\EE_n$ algebras.
\end{enumerate}
\end{thm}

@@

\begin{lmm}
For a closed $n$-dimensional manifold~$M$, 
\begin{align*}
\int_M \UU_n(\frak{gl}_\infty)
&\simeq \cliels(\Omega^\bu(M) \otimes \fgl_\infty) \\
&\simeq \Sym(\Cyc_\bu(\Omega^\bu(M))[1]) \\
&\simeq \Sym(\Omega^\bu(LM/^h S^1))[1])).
\end{align*}
\end{lmm}

@@

\begin{lmm}
For a closed $n$-dimensional manifold~$M$, 
\[
\clies(\fgl_\infty \otimes \Omega^\bu(M), \cliels(\fgl_\infty \otimes \Omega^\bu(M)) \simeq \End^\bullet(\Sym(\Omega^\bu(LM/^h S^1))[1])))
\]
where the left hand side is the factorization homology of $\EE_n$ center ${\frak Z}_n(\fgl_\infty)$ and the right hand side is the $\EE_0$ center of the factorization homology of~$\UU_n \fgl_\infty$.
\end{lmm}

>>>>

\begin{thm}
\label{T:compcentralizer}
Let $f: \fg \rightsquigarrow \fh$ and $g: \fh \rightsquigarrow \fl$ be maps of  $L_\infty$ algebras,
and let $\bold{f}: \bU_n \fg \to \bU_n \fh$ and $\bold{g}: \bU_n \fh \to \bU_n \fl$ denote the induced maps of factorization algebras.
\begin{enumerate} 
\item There is a natural map of factorization algebras
\[
(-\star-) : \bZ_n(g) \otimes \bZ_n(f) \to \bZ_n(g \circ f),
\]
given by definition~\ref{def:comp}, 
that models the canonical map 
\[
{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f).
\] 
\item If $f= \fg \stackrel{\id}\to \fg$, 
then the composition $(-\star-)$ makes $\bZ_n(\fg)$ into an 
augmented associative algebra {\em on the nose} in the 1-category of factorization algebras on~$\RR^n$,
and it models the center ${\frak Z}_n(\fg)$ as an $\EE_1$ algebra in $\EE_n$ algebras.
\end{enumerate}
\end{thm}

@@

\begin{lmm}
For a closed $n$-dimensional manifold~$M$, 
\begin{align*}
\int_M \UU_n(\frak{gl}_\infty)
&\simeq \cliels(\fgl_\infty(\Omega^\bu(M) )) \\
&\simeq \Sym(\Cyc_\bu(\Omega^\bu(M))[1]) \\
&\simeq \Sym(\Omega^\bu(LM/^h S^1))[1])).
\end{align*}
\end{lmm}

@@

\begin{lmm}
For a closed $n$-dimensional manifold~$M$, 
\[
\clies(\fgl_\infty(\Omega^\bu(M)), \cliels(\fgl_\infty (\Omega^\bu(M))) \simeq \End^\bullet(\Sym(\Omega^\bu(LM/^h S^1))[1])))
\]
where the left hand side is the factorization homology of $\EE_n$ center ${\frak Z}_n(\fgl_\infty)$ and the right hand side is the $\EE_0$ center of the factorization homology of~$\UU_n \fgl_\infty$.
\end{lmm}
